Nilpotent Invariants \\ for Generic Discrete Series of Real Groups

### 2024-10-02 whittaker.tex
almost finished

\renewcommand{\t}{\mathfrak t}
\newcommand{\su}{\mathfrak s\mathfrak u}
\newcommand{\g}{\mathfrak g}
\newcommand{\gder}{\mathfrak g_{\mathrm{der}}}
\newcommand\inv{^{-1}}
\newcommand\wh{\widehat}
\newcommand{\GL}{\text{GL}}
\newcommand{\SL}{\text{SL}}
\newcommand{\SO}{\text{SO}}
\newcommand{\SU}{\text{SU}}
\newcommand{\Spin}{\text{Spin}}
\newcommand{\chGGamma}{\phantom{a}^\vee G^\Gamma}
\newcommand{\GGamma}{G^\Gamma}
\newcommand{\s}{\mathfrak s}
\newcommand{\w}{\mathfrak w}
\newcommand{\AV}{\mathrm{AV}}
\newcommand{\KS}{\mathrm{KS}}
\newcommand{\Wh}{\mathrm{Wh}}
\newcommand{\WF}{\mathrm{WF}}
\newcommand{\AC}{\mathrm{AC}}
\newcommand{\AVann}{\mathrm{AV}_{\mathrm{ann}}}
\newcommand{\GK}{\mathrm{GK}}
\newcommand{\Op}{\O_p}
\newcommand{\Kostant}[1]{\mathcal{K}(#1)}
\newcommand{\ECom}{\mathcal{E}^{\mathcal{C}}_\Omega}
\begin{document}
\title{Nilpotent Invariants \\ for Generic Discrete Series of Real Groups}
\author{Jeffrey Adams \& Alexandre Afgoustidis}
\maketitle

@@

\begin{lemma}
\label{l:pi_to_av}
  \label{l:AV}
Suppose $\pi$ is a generic discrete series representation with Harish-Chandra parameter $\lambda\in\t^*$.
Set

@@

\begin{corollary}
\label{c:same}
Suppose $\pi$ is a generic discrete series representation with Harish-Chandra parameter $\lambda$.
Then $\AV(\pi)$, $\WF(\pi)$ and $\Wh(\pi)$ only depend on the Weyl chamber of $\lambda$.
\end{corollary}

@@

\begin{proof}
If  $\mathscr{C}, \mathscr{C}'$ are in the same $W_K$-orbit, then the Harish-Chandra parameters of $\pi$, $\pi'$ have representatives in the same Weyl chamber; therefore $\Wh(\pi)=\Wh(\pi')$ by Corollary \ref{c:same}.

>>>>

\renewcommand{\t}{\mathfrak t}
\newcommand{\su}{\mathfrak s\mathfrak u}
\newcommand{\g}{\mathfrak g}
\newcommand{\gder}{\mathfrak g_{\mathrm{der}}}
\newcommand\inv{^{-1}}
\newcommand\wh{\widehat}
\newcommand{\GL}{\text{GL}}
\newcommand{\SL}{\text{SL}}
\newcommand{\SO}{\text{SO}}
\newcommand{\SU}{\text{SU}}
\newcommand{\Spin}{\text{Spin}}
\newcommand{\chGGamma}{\phantom{a}^\vee G^\Gamma}
\newcommand{\GGamma}{G^\Gamma}
\newcommand{\s}{\mathfrak s}
\newcommand{\w}{\mathfrak w}
\newcommand{\AV}{\mathrm{AV}}
\newcommand{\KS}{\mathrm{KS}}
\newcommand{\Wh}{\mathrm{Wh}}
\newcommand{\WF}{\mathrm{WF}}
\newcommand{\AC}{\mathrm{AC}}
\newcommand{\AVann}{\mathrm{AV}_{\mathrm{ann}}}
\newcommand{\GK}{\mathrm{GK}}
\newcommand{\Op}{\O_p}
\newcommand{\Kostant}[1]{\mathcal{K}(#1)}
\newcommand{\ECom}{\mathcal{E}^{\mathcal{C}}_\Omega}
\begin{document}
%Jeffrey Adams University of Maryland/IDA Center for Computing Sciences
%jda@math.umd.edu
\title{Nilpotent Invariants \\ for Generic Discrete Series of Real Groups}
\author{Jeffrey Adams \& Alexandre Afgoustidis}
\maketitle

@@

\begin{lemma}
\label{l:pi_to_av}
  \label{l:AV}
Suppose $\pi$ is a generic discrete series representation and $\lambda\in\t^*$ is a representative of its  Harish-Chandra parameter.
Set

@@

\begin{corollary}
\label{c:same}
Suppose $\pi,\pi'$ are generic discrete series representations. Let  $\lambda,\lambda'$ be representatives
for the Harish-Chandra parameters of $\pi,\pi'$. If 
$\lambda,\lambda'$ are in the same  Weyl chamber then
$\pi,\pi'$ have the same associated variety, wave-front set, and Whittaker models.
\end{corollary}

@@

\begin{proof}
If  $\mathscr{C}, \mathscr{C}'$ are in the same $W_K$-orbit, then the Harish-Chandra parameters of $\pi$, $\pi'$ have representatives in the same Weyl chamber; therefore $\Wh(\pi)=\Wh(\pi')$ by Corollary~\ref{c:same}.
